Pillar 1 - Sequential Pattern Mining

### 2019-02-20 Pillar 1 - Sequential Pattern Mining.Rmd
filter rules based on count, lift and confidence

  # lhs not, rhs low
  filter(
    str_detect(rhs, "fail"),
    lift > 1,
    confidence >= 0.40
    )
```

@@

  # constraints to respect
  filter(
    str_detect(rhs, "low"),
    lift > 1,
    confidence >= 0.40
    )
```

@@

  # Reduce number of rules
  filter(
    # exclude rules with same course on lhs and rhs
    lhs_course != rhs_course,
    # rhs is grade less than or equal to 6
    rhs_outcome == 6
    ) %>%

  # for each combination of course (lhs and rhs), keep AR with highest lift (most informative)
  group_by(
    lhs_course,
    rhs_course
    ) %>%
  top_n(
    n = 1,
    lift
    ) %>%
  ungroup
```

@@

    filter(
      count >= 10
      )

>>>>

  # lhs not, rhs low
  filter(
    str_detect(rhs, "fail")
    )
```

@@

  # constraints to respect
  filter(
    str_detect(rhs, "low")
    )
```

@@

  # Reduce number of rules
  filter(
    # exclude rules with same course on lhs and rhs
    lhs_course != rhs_course,
    # rhs is grade less than or equal to 6
    rhs_outcome <= 6,
    lhs_outcome <= 7
    )
```

@@

    filter(
      count      >= 10,
      lift       >= 1,
      confidence >= 0.4
      )
